MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-25 MAESTROeX_I/results.tex
saving progress

\subsection{AMR Performance}
Show 3D reacting bubble rise performance.
Show 3-level spherical performance (stats won't be as good but explain why: refining a larger percentage of grid)

\subsection{Scaling}
In Figure XXX we show weak scaling results for convection preceding ignition in a spherical, full-star sub-Chandrasekhar mass white dwarf.
These results are representative of simulations used in actual scientific studies; see \cite{MAESTRO_convection,MAESTRO_AMR}.
For this scaling study we use a spatially uniform grid (no AMR).

@@

We compare the original BoxLib-based MAESTRO implementation to the AMReX MAESTROeX implementation with the classic algorithm (original temporal integrator).

We also include a plot of MAESTROeX without base state evolution.

@@

\MarginPar{Making new plots splitting out projections vs. everything else.}

@@

>>>>

\subsection{Performance and Scaling}
In Figure \ref{fig:scaling} we show weak scaling results for simulations of convection preceding ignition in a spherical, full-star sub-Chandrasekhar mass white dwarf.
We emphasize that these results are obtained using simulations used in actual scientific studies; see \cite{MAESTRO_convection,MAESTRO_AMR}.
For this scaling study we use a spatially uniform grid (no AMR).

@@

We compare the original BoxLib-based MAESTRO implementation to the AMReX MAESTReX implementation with the same algorithm.
We also include a plot of MAESTROeX without base state evolution.

For the new temporal algorithm, and the option for irregular base state mapping, <COMMENT HERE ABOUT RUNTIME>

@@

@@

\subsection{AMR Performance}
Show 3D reacting bubble rise performance.
Show 3-level spherical performance (stats won't be as good but explain why: refining a larger percentage of grid)
Images of grid configuration.
